---
title: "Subjective mental state and Fatigue, an Investigation into possible paradoxical effects"
output: 
  html_document:
    code_folding: show
    theme:
      bg: "#202123"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
---

```{r setup, include=FALSE}
# Tidyverse set-up
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
# Libraries
set.seed(2023)
library(tidyverse)
library(readxl)
# Datasets
vas_new <- read_csv("data/main_outcome.csv")
vas_old <- read_excel("data/demographic_comparison.xlsx")
# Tidying
vas_new_selection <- vas_new %>%
  mutate(selection = case_when(suspicion == "yes" ~ "yes",
    `qualitative exclusion` == "yes" ~ "yes",
    TRUE ~ "no"),
    experiment = "control") %>%
  select(selection, CON_full, sleep, pr_vas, po_vas, vas_change, experiment)

vas_old_selection <- vas_old %>%
  rename(pr_vas = `pre-vas`, po_vas = `post-vas`, vas_change = `dif-vas`) %>%
  mutate(selection = "no",
    experiment = "experimental") %>%
  select(selection, age, sleep, pr_vas, po_vas, vas_change, experiment)
# Joining
vas_all <- vas_new_selection %>%
  full_join(vas_old_selection)
```

Investigation of the questions as set out in the [pre-registration](https://osf.io/fybc9).

# VAS difference confirmation {.tabset}

## Self-aware excluded

n = 12.

Phrases leading to exclusion:

* 20007: `r vas_new$report[3]`
* 20002: `r vas_new$report[8]`

Are the two experiments different?

```{r include=FALSE, warning=FALSE}
# Clean away self-selected leavers
vas_all_clean_model <- vas_all %>%
  filter(selection == "no") %>%
  mutate(experiment = recode(experiment, `experimental` = 1, `control` = 0))

model <- lm(vas_change ~ experiment, vas_all_clean_model)
```

```{r echo=FALSE, warning=FALSE}
vas_all_clean_plot <- vas_all %>%
  filter(selection == "no")

p <- ggplot(vas_all_clean_plot, aes(experiment, vas_change, fill=experiment)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot() +
  geom_jitter() +
  scale_fill_viridis_d()
```


```{r echo=FALSE, warning=FALSE}
p
```


```{r echo=FALSE, warning=FALSE}
summary(model)
```

## Older excluded

Phrases leading to exclusion:

* 20007: `r vas_new$report[3]`
* 20002: `r vas_new$report[8]`

Are the two experiments different?

```{r include=FALSE, warning=FALSE}
# Clean away self-selected leavers
vas_all_clean_model <- vas_all %>%
  filter(age < 30 | is.na(age)) %>%
  filter(selection == "no") %>%
  mutate(experiment = recode(experiment, `experimental` = 1, `control` = 0))

model <- lm(vas_change ~ experiment, vas_all_clean_model)
```

```{r echo=FALSE, warning=FALSE}
vas_all_clean_plot <- vas_all %>%
  filter(selection == "no") %>%
  filter(age < 30 | is.na(age))

p <- ggplot(vas_all_clean_plot, aes(experiment, vas_change, fill=experiment)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot() +
  geom_jitter() +
  scale_fill_viridis_d() +
  ylab("VAS change")
```


```{r echo=FALSE, warning=FALSE}
p
```


```{r echo=FALSE, warning=FALSE}
summary(model)
```

## All

n = 16.

Are the two experiments different?

```{r include=FALSE, warning=FALSE}
# Clean away self-selected leavers
vas_all_clean_model <- vas_all %>%
  mutate(experiment = recode(experiment, `experimental` = 1, `control` = 0))

model <- lm(vas_change ~ experiment, vas_all_clean_model)
```

```{r echo=FALSE, warning=FALSE}
vas_all_clean_plot <- vas_all

p <- ggplot(vas_all_clean_plot, aes(experiment, vas_change, fill=experiment)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot() +
  geom_jitter() +
  scale_fill_viridis_d() +
  ylab("VAS change")
```


```{r echo=FALSE, warning=FALSE}
p 
```


```{r echo=FALSE, warning=FALSE}
summary(model)
```

# Control Experiment {.tabset}

## Self-aware excluded

```{r echo=FALSE, warning=FALSE}
vas_test <- vas_all %>%
  filter(selection == "no", experiment == "control")

model <- t.test(vas_test$po_vas, vas_test$pr_vas, alternative = "greater")
```

```{r echo=FALSE}
model
```

```{r echo=FALSE, warning=FALSE}
vas_test_clean_plot <- vas_test %>%
  select(pr_vas, po_vas) %>%
  pivot_longer(1:2, names_to = "timepoint", values_to = "vas") %>%
  mutate(timepoint = recode(timepoint,pr_vas = "before", po_vas = "after"))

p <- ggplot(vas_test_clean_plot, aes(reorder(timepoint, vas), vas, fill=timepoint)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot() +
  geom_jitter() +
  scale_fill_viridis_d() +
  xlab("Timepoint") +
  ylab("VAS")
```


```{r echo=FALSE, warning=FALSE}
p
```

## All

```{r echo=FALSE, warning=FALSE}
vas_test <- vas_all %>%
  filter(experiment == "control")

model <- t.test(vas_test$po_vas, vas_test$pr_vas, alternative = "greater")
```

```{r echo=FALSE}
model
```

```{r echo=FALSE, warning=FALSE}
vas_test_clean_plot <- vas_test %>%
  select(pr_vas, po_vas) %>%
  pivot_longer(1:2, names_to = "timepoint", values_to = "vas") %>%
  mutate(timepoint = recode(timepoint,pr_vas = "before", po_vas = "after"))

p <- ggplot(vas_test_clean_plot, aes(reorder(timepoint, vas), vas, fill=timepoint)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot() +
  geom_jitter() +
  scale_fill_viridis_d() +
  xlab("Timepoint") +
  ylab("VAS")
```


```{r echo=FALSE, warning=FALSE}
p
```

# Personality effects

No relation to conscienciousness.

```{r echo=FALSE, warning=FALSE}
model <- lm(vas_change ~ CON_full, vas_test)
```

```{r echo=FALSE}
summary(model)
```